Technical Paper Proposal: \\ Placement Algorithms for Heterogenous FPGAs

### 2024-09-12 docs/proposal/proposal.tex
final touches

\section{Proposal}
A compiler takes a program written in high-level programming language like a Java or Python and assembles low-level machine code which is ready to be executed on a CPU.
In similar fashion, an Electronic Design Automation tool (EDA) takes a high-level description of a digital system written in Verilog or VHDL and produces a bitstream which is ready to be deployed to an FPGA.
In a superficial way, compilers and EDAs perform the same task for engineers but in different industries. 
One for software, the latter for hardware.

@@

Second, it will briefly explore the historical progress made on placement algorithms for both VLSI and FPGA and then explore the current trends in placement research.

Then third, the paper will outline my own work on placement strategies, whether they be reproductions of existing strategies, or if I manage to think of a novel strategy. 
I intend to use Xilinx's open-source API, RapidWright, which is written in Java and provides backend access to Xilinx's FPGA EDA, Vivado.

@@

\newpage
\bibliographystyle{ieeetr}
\nocite{*}
\bibliography{
    references/surveys,
    references/rapidwright,
    references/fpga_placement,
    references/vlsi_placement,
}
\end{document}

>>>>

\section{Proposal}
    A compiler takes a program written in high-level programming language like a Java or Python and assembles low-level machine code which is ready to be executed on a CPU.
    In similar fashion, an Electronic Design Automation tool (EDA) takes a high-level description of a digital system written in Verilog or VHDL and produces a bitstream which is ready to be deployed to an FPGA.
    In a superficial way, compilers and EDAs perform the same task for engineers but in different industries. 
    One for software, the other for hardware.

@@

    Second, it will briefly explore the historical progress made on placement algorithms for both VLSI and FPGA and then explore the current trends in open-source placement research 
    \cite{Yosys}, \cite{AMFPlacer2}, \cite{RapidLayout}, \cite{RapidStream}, \cite{DREAMPlace}, \cite{DREAMPlaceFPGA}.
    I would have liked to explore the current trends in proprietary EDAs but they are unfortunately closed source.

    Then third, the paper will outline my own work on placement strategies, whether they be reproductions of existing strategies, or a novel strategy if I manage to think of one (unlikely). 
    I intend to use Xilinx's open-source API, RapidWright, which is written in Java and provides backend access to Xilinx's FPGA EDA, Vivado. 
    I have already familiarized myself with the API and, over the past month have practiced using the Vivado + RapidWright toolchain to do basic tasks like extracting the netlist of a synthesized VHDL design.
    You can see my preliminary work in my Github: \url{https://github.com/TotoroTron/place-and-route}.

@@

    \newpage
    \bibliographystyle{ieeetr}
    \nocite{*}
    \bibliography{
        references/surveys,
        references/rapidwright,
        references/fpga_placement,
        references/vlsi_placement,
    }

\end{document}
